Draft Exploration

### 2020-04-12 draft_exploration.Rmd
added intro to shiny
working on shiny about page

```{r, echo=FALSE}
draft_2000_2012 <- draft %>%
  filter(year >= 2000 & year <= 2012)

draft_2000_2012 <- draft_2000_2012 %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(draft_round) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(draft_2000_2012, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  labs(
    x = "Draft Round",
    y = "Percent to reach Major Leagues",
    title = "Percent of Draft Picks by Round to Reach the Majors",
    subtitle = "Data from 2000-2012 drafts"
  ) 
```

```{r, echo=FALSE}
grow_talent <- master %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(decade = ifelse(year %in% 1970:1979, 1970,
                                 ifelse(year %in% 1980:1989, 1980,
                                        ifelse(year %in% 1990:1999, 1990,
                                               ifelse(year %in% 2000:2009, 2000,
                                                      ifelse(year %in% 2010:2019, 2010, NA)))))) %>%
  filter(year >= 1980 & year <= 2009) %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(teamname) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

@@

ggplot(hs_signed_90_09, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Round",
    y = "Percent of Signed High School Picks to MLB",
    title = "Percent of Signed High School Picks to MLB by Round",
    subtitle = "Data: 1980-2009 Drafts"
  )

>>>>

```{r, echo=FALSE}
draft_2000_2012 <- draft %>%
  filter(year >= 1990 & year <= 2011)

draft_2000_2012 <- draft_2000_2012 %>%
  filter(!is.na(high_level)) %>%
  filter(draft_round <= 50) %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(draft_round) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(draft_2000_2012, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  labs(
    x = "Draft Round",
    y = "Percent to reach Major Leagues",
    title = "Percent of Draft Picks by Round to Reach the Majors",
    subtitle = "Data from 1990-2011 drafts"
  ) 
```

```{r, echo=FALSE}
grow_talent <- master %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(decade = ifelse(year %in% 1970:1979, 1970,
                                 ifelse(year %in% 1980:1989, 1980,
                                        ifelse(year %in% 1990:1999, 1990,
                                               ifelse(year %in% 2000:2009, 2000,
                                                      ifelse(year %in% 2010:2019, 2010, NA)))))) %>%
  filter(year >= 1980 & year <= 2009) %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(teamname) %>%
  summarize(mlb = sum(mlb_made), 
            total = sum(ignore),
            percent_mlb = sum(mlb_made) / sum(ignore))

@@

ggplot(hs_signed_90_09, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Round",
    y = "Percent of Signed High School Picks to MLB",
    title = "Percent of Signed High School Picks to MLB by Round",
    subtitle = "Data: 1990-2009 Drafts"
  )

```{r, echo=FALSE}
college_signed <- master %>%
  filter(source == "C" & signed == "Y") %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0))

college_signed_90_09 <- college_signed %>%
  mutate(ignore = 1) %>%
  group_by(draft_round) %>%
  filter(year >= 1990 & year <= 2009) %>%
  filter(draft_round <= 40) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(college_signed_90_09, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Round",
    y = "Percent of College Picks to MLB",
    title = "Percent of Signed College Picks to MLB by Round",
    subtitle = "Data: 1990-2009 Drafts"
  )
